---
title: 'Peer-graded Assignment: Statistical Inference Course Project'
author: "Aditya Lahiri"
date: "February 14, 2018"
output:
  word_document: default
  pdf_document: default
---
Overview: This report contains solutions to two parts of the coursera final project on statistical inference.
Some statistical inference and basic analysis has been performed to achieve the result of the simultion.
# PART 1  
```{r}
set.seed(10234)
lambda <- 0.2
n <- 40
sims <-1000
data<-replicate(sims,rexp(n, lambda))
mean_data <-colMeans(data)
```
The sample mean is 
```{r}
mean(mean_data)
```
The theoretical mean is
```{r}
print(1/lambda)
```
The following graph provides a visualization for the simulation carried out in the code aboveGreen is for the theoretical mean and red is for the sample mean
```{r}
hist(mean_data, xlab = "mean", main = "Sample Mean versus Theoretical Mean")
abline(v =mean(mean_data) , col = "red")
abline(v =1/lambda , col = "green")
```
The sample mean is 4.975896 (red) and the theoretical mean is 5 (green) and hence they are very close to each other. 
```{r}
std_dev_sample <- sd(mean_data)
std_dev_theor <- (1/lambda)/sqrt(n)
var_sample <- std_dev_sample^2
var_theor <- std_dev_theor^2
```
The sample variance is :
```{r}
var_sample
```
The Theoretical variance is:
```{r}
var_theor
```
The sample and theoretical variance are very close.
```{r}
x <- seq(min(mean_data), max(mean_data), length=100)
y <- dnorm(x, mean=1/lambda, sd=(1/lambda/sqrt(n)))
hist(mean_data,breaks=n,prob=T,col="red",xlab = "means",main="Density of means",ylab="density")
lines(x, y, pch=22, col="black", lty=5)
sample_conf_interval <- round (mean(mean_data) + c(-1,1)*1.96*sd(mean_data)/sqrt(n),3)
theory_conf_interval <- (1/lambda) + c(-1,1)*1.96*sqrt(var_theor)/sqrt(n)
```
From the plot above we see the distribution follows a normal distribution. 
Also note that the theoretical 95% confidence interval is:
```{r}
theory_conf_interval
```
and the sample 95% confidence interval is:
```{r}
sample_conf_interval
```
The confidence intervals are close enough. The following is the qq plot.
```{r}
qqnorm(mean_data); qqline(mean_data)
```
The theoretical quantiles match closely with the sample quantiles, so all these test prove the distribution is normal.


